\Title

### 2021-06-15 manuscript/content.tex
Move damping text and add Martinez and Li (2016)
Fix typo and move explanation about damping to where it's first
introduced.

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
Using a dimensionless damping parameter allows us to narrow the range of values
of $\lambda$ that would generate the most accurate predictions, irrespective
of the dataset and its units.
The damping parameter controls the amount of regularization that is be applied:
a large damping value would generate smooth solutions that fail to reproduce
the high frequency components, while a small value would overfit the data,
failing to produce realistic interpolation results.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-6}$ and $10^{4}$ varying by order-of-magnitude, irrespective of the
dataset.
The choice of the damping and any other hyper-parameter could be done through
validation methods, such as cross-validation algorithms.

>>>>

\noindent where
$\mathbf{W}$ is a $N \times N$ diagonal matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.
The damping parameter controls the amount of regularization that will be applied:
a large damping value would generate smooth solutions that fail to reproduce
the high frequency components, while a small value would overfit the data,
failing to produce realistic interpolation results \citep{martinez2016}.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
Using a dimensionless damping parameter allows us to narrow the range of values
of $\lambda$ that would generate the most accurate predictions, irrespective
of the dataset and its units.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-6}$ and $10^{4}$ varying by order-of-magnitude.
The choice of the damping and other hyper-parameters like the source depth
could be done through well-established statistical methods, such as
cross-validation.
